\bf Model Visualization Techniques for a Social Network Model

### 2017-06-30 paper.Rnw
add a to-do list

\hh{shouldn't that be independence? - make the conditional independence assumption above a labelled formula (e.g. C1) and then call it here }
Because of the conditional independence assumptions in Equation~\ref{eq:c1}, we can consider the objective function for each node separately, since only one tie from one node is changing at a time. The objective function is then written as 
\begin{equation} \label{eq:of1}
f_i(\boldsymbol{\beta}, x) = \sum_k \beta_k s_{ik}(x, \mathbf{Z}),
\end{equation}

@@

The top row of Figure~\ref{makinggif} shows an edge being removed, and the bottom row shows one being added. In both cases, the ego nodes chosen to act change color from black to red, and they also increase greatly in size. In the case of an edge being removed, the edge that currently exists is emphasized with the color and size change that the node also gets, and as the animation proceeds the edge shrinks to disappearing, while the node shrinks and changes color back to the original black. If the edge is being added, it appears colored red from nothing and grows to a large size, then changes color to match the rest of the edges, while the node shrinks and changes color to match the other nodes.

>>>>

%\hh{shouldn't that be independence? - make the conditional independence assumption above a labelled formula (e.g. C1) and then call it here }
Because of the conditional independence assumptions in Equation~\ref{eq:c1}, we can consider the objective function for each node separately, since only one tie from one node is changing at a time. The objective function is then written as 
\begin{equation} \label{eq:of1}
f_i(\boldsymbol{\beta}, x) = \sum_k \beta_k s_{ik}(x, \mathbf{Z}),
\end{equation}

@@

The top row of Figure~\ref{fig:makinggif} shows an edge being removed, and the bottom row shows one being added. In both cases, the ego nodes chosen to act change color from black to red, and they also increase greatly in size. In the case of an edge being removed, the edge that currently exists is emphasized with the color and size change that the node also gets, and as the animation proceeds the edge shrinks to disappearing, while the node shrinks and changes color back to the original black. If the edge is being added, it appears colored red from nothing and grows to a large size, then changes color to match the rest of the edges, while the node shrinks and changes color to match the other nodes.
